Tackling discrepancies in freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution

### 2021-02-18 Paper/Draft_harmonization_paper.tex
18.02: Formatting fixes

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{float}
\usepackage[table,xcdraw]{xcolor}
\usepackage{color, colortbl}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{rotating}
\usepackage{caption}
\usepackage{authblk}
\graphicspath{{Figures/}}
\usepackage{rotating}
\usepackage{geometry}
\usepackage{array}
\usepackage{lscape}
\usepackage{longtable}
\usepackage{hhline}
\usepackage{lmodern}
\usepackage[
backend = biber,
natbib,
style = apa,
citestyle = authoryear,
maxcitenames = 2, 
maxbibnames = 99, 
uniquename=false,
uniquelist=false
%sorting = none % sort by name year title
]{biblatex}
\addbibresource{Ref_invertebrate_DB.bib}

@@

% functions and definitions
\definecolor{Gray}{gray}{0.9}

@@

%%%%% New Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Tackling discrepancies in freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution}
\author[1]{Stefan Kunz}
\author[2]{Ben J. Kefford}
\author[3]{Astrid Schmidt-Kloiber}
\author[4]{Christoph D. Matthaei}
\author[5]{Philippe Usseglio-Polatera}
\author[4]{Wolfram Graf}
\author[6]{N. LeRoy Poff}
\author[7]{Leon Metzeling}
\author[8]{Laura Twardochleb}
\author[9]{Charles P. Hawkins}
\author[1]{Ralf B. Schäfer}
\affil[1]{Institute for Environmental Sciences, University of Koblenz-Landau, Landau, Germany}
\affil[2]{Centre for Applied Water Science, Institute for Applied Ecology, University of Canberra, Canberra, Australia}
\affil[3]{Institute of Hydrobiology and Aquatic Ecosystem Management, University of Natural Resources and Life Sciences Vienna (BOKU), Vienna, Austria}
\affil[4]{Department of Zoology, University of Otago, Dunedin, New Zealand}
\affil[5]{University of Lorraine, CNRS, LIEC, Metz, France}
\affil[6]{Department of Biology, Colorado State University, Fort Collins, USA}
\affil[7]{Environment Protection Authority Victoria, Applied Sciences Division, Macleod, Australia}
\affil[8]{Department of Fisheries and Wildlife, Michigan State University, East Lansing, USA}
\affil[9]{Department of Watershed Sciences and the Ecology Center, Utah State University, Logan, USA}
\date{}

@@

\begin{table}[H]
\centering

@@

\begin{tabular}{lll}
Grouping feature & Trait & Combined traits\\

@@

\end{tabular}
\end{table}

@@

For our study aim of comparing the effects of different aggregation methods on trait–environment relationship inference, we aggregated the traits of two of the harmonised datasets to the family level.
We used three different aggregation approaches: (1) direct aggregation of taxa to family level with either the median or mean, giving equal weight to every taxon. We denote these aggregation methods as \textit{direct\_agg\textsubscript{median}} and \textit{direct\_agg\textsubscript{mean}}, respectively; (2) stepwise aggregation, first to the genus level and subsequently to the family level with either the median or mean. This approach gives equal weights to each genus. Hereafter, we denote this aggregation type as \textit{stepwise\_agg\textsubscript{median}} or \textit{stepwise\_agg\textsubscript{mean}}, respectively; and (3) aggregation using a weighted mean approach, denoted as \textit{weighted\_agg}. This method weights each genus according to its number of species in the trait datasets, regardless of whether information was available for every used grouping feature (Figure \ref{fig:data_proc_overview}). When we refer to \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg} together we denote these methods as mean aggregation methods and when we refer to \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}} together, we denote these methods as median aggregation methods.

@@

\subsection*{Effects of harmonisation and trait aggregation on trait-environment relationship inferences}

To further evaluate the effects of grouping-feature harmonisation and trait aggregation on characterisation of trait–environment relationships, we repeated the analysis of \citet{szocs_effects_2014}, who studied the effects of anthropogenic salinisation on invertebrates in the River Werra in Germany. The River Werra has been subject to effluents from the potash industry since the mid- 20th century, which makes it a useful system for studying the responses of invertebrates and their trait compositions to salinisation (\cite{bathe_biological_2011}). \citet{szocs_effects_2014}  used redundancy analysis (RDA) to compare trait compositions among sites downstream, upstream, and close to salt discharge (transition). Further details about the original study can be found in \citet{szocs_effects_2014}.

@@

\begin{table}[ht]
    \centering
    \caption{Number (Nr.) of taxa per harmonised dataset and per taxonomic level. Numbers in parenthesis show rounded relative frequencies in percent.} 
    \label{tab:tax_coverage}
    \begin{tabular}{lccccc}
    \toprule[.1em]
    Dataset & Taxa (Nr.) & Aquatic insects (Nr.) & Species & Genus & Family \\ 
    \toprule[.1em]
    EU & 4601 & 3942 (86) & 3739 (81) & 704 (15) & 158 (3) \\ 
    NOA & 3753 & 3305 (88) & 2414 (64) & 1163 (31) & 176 (5)  \\ 
    AUS & 1402 & 1016 (72) & 564 (40) & 578 (41) & 260 (19) \\ 
    NZ & 478 & 443 (93) & 404 (85) & 47 (10) & 27 (6) \\ 
    \bottomrule
    \end{tabular}
\end{table}
\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
\centering
Abbreviations: EU, European; NOA, North American; AUS, Australian; NZ, New Zealand.
}
\end{minipage}

@@

\begin{table}[ht]
    \centering
    \caption{Rounded percentage of entries that include 
    information for the individual grouping features
    shown per trait dataset.} 
    \label{tab:trait_coverage}
    \begin{tabular}{lccccccc}
    \toprule[.1em]
    Dataset & Body form & Oviposition & Voltinism & Locomotion & Size & Respiration & Feeding mode \\ 
    \toprule[.1em]
    EU & 8 & 15 & 23 & 36 & 11 & 57 & 76 \\ 
    NOA & 28 & 13 & 47 & 52 & 73 & 44 & 63 \\ 
    AUS & 4 & 46 & 49 & 39 & 75 & 68 & 99 \\ 
    NZ & 100 & 94 & 100 & 99 & 100 & 100 & 99 \\ 
    \bottomrule
    \end{tabular}
\end{table}
\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
\centering
Abbreviations: EU, European; NOA, North American; AUS, Australian; NZ, New Zealand.
}
\end{minipage}

@@

\begin{minipage}{\linewidth}\small

@@

\begin{table}[H]
  \centering
  \caption{Percentage of differing cases, minimum, maximum, mean, and standard deviation of absolute differences between trait affinities assigned at family level by experts and aggregated trait affinities from five different aggregation methods.}
  \label{tab:summary_stat_aggr_vs_fam_assigned}
  \begin{tabular}{ll|ccccc}
  \toprule[.1em]
  Database & \specialcell{Comparison to\\ traits at family level} & \specialcell{Differing \\ cases [\%]} & \specialcell{Min. \\ differences} & \specialcell{Max. \\ differences} & \specialcell{Mean abs. \\ differences} & \specialcell{SD abs. \\ differences} \\ 
  \toprule[.1em]
  \multirow{4}{*}{\specialcell{Australia}} & \specialcell{\textit{direct\_agg (median)}} & 16.53 & 0.01 & 1.00 & 0.45 & 0.27 \\ 
  & \specialcell{\textit{direct\_agg (mean)}} & 23.24 & $< 0.01$ & 0.99 & 0.34 & 0.23 \\ 
  & \specialcell{\textit{stepwise\_agg (median)}} & 17.90 & 0.01 & 1.00 & 0.42 & 0.26 \\ 
  & \specialcell{\textit{stepwise\_agg (mean)}} & 23.24 & $< 0.01$ & 0.99 & 0.33 & 0.22 \\ 
  & \specialcell{\textit{weighted\_agg}} & 23.24 & $< 0.01$ & 1.00 & 0.34 & 0.24 \\ 
  \midrule
  \multirow{4}{*}{\specialcell{North America}} & \specialcell{\textit{direct\_agg (median)}} & 15.33 & 0.17 & 1.00 & 0.70 & 0.26 \\ 
  & \specialcell{\textit{direct\_agg (mean)}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.26 \\ 
  & \specialcell{\textit{stepwise\_agg (median)}} & 18.00 & 0.08 & 1.00 & 0.63 & 0.28 \\ 
  & \specialcell{\textit{stepwise\_agg (mean)}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.27 \\ 
  & \specialcell{\textit{weighted\_agg}} & 47.00 & $< 0.01$ & 1.00 & 0.31 & 0.28 \\ 
  \bottomrule
  \end{tabular}
\end{table}
\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
  \centering
  Abbreviations: Min., Minimum; Max., Maximum; abs., absolute; SD, Standard deviation.
  }
  \end{minipage}

@@

\subsection*{Effects of harmonisation and trait aggregation on trait-environment relationships}

@@

\section*{Author contribution}
R.B.S. and S.K. designed the study; B.J.K. and L.M. provided trait data for Australia; P.U-P. provided trait data from the Tachet database; C.P.H., N.L.P., and L.T. provided trait data for North America; C.D.M. provided trait data for New Zealand;
B.J.K., A.S-K., C.D.M, W.G., N.L.P., L.M., and C.P.H. provided in depth information on trait data and discussed procedure of analysis; S.K. conducted data processing and the statistical analyses.; S.K. wrote the manuscript; B.J.K, A-S.K., C.D.M, P.U-P., C.P.H., and R.B.S. discussed the results and provided suggestions on the manuscript.

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{float}
\usepackage[table,xcdraw]{xcolor}
\usepackage{color, colortbl}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{rotating}
\usepackage{caption}
\usepackage{authblk}
\usepackage{csquotes}
\graphicspath{{Figures/}}
\usepackage{setspace}
\usepackage{rotating}
\usepackage{geometry}
\usepackage{array}
\usepackage{lscape}
\usepackage{longtable}
\usepackage{hhline}
\usepackage{lmodern}
\usepackage[
backend = biber,
natbib,
style = apa6,
citestyle = authoryear,
maxcitenames = 2, 
maxbibnames = 99, 
uniquename=false,
uniquelist=false
%sorting = none % sort by name year title
]{biblatex}
\addbibresource{Ref_invertebrate_DB.bib}

@@

%%%% Functions and definitions %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\definecolor{Gray}{gray}{0.9}

@@

%%%%% New Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%% Formatting options %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\onehalfspacing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Tackling discrepancies in freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution}
\author[1]{Stefan Kunz}
\author[2]{Ben J. Kefford}
\author[3]{Astrid Schmidt-Kloiber}
\author[4]{Christoph D. Matthaei}
\author[5]{Philippe Usseglio-Polatera}
\author[3]{Wolfram Graf}
\author[6]{N. LeRoy Poff}
\author[7]{Leon Metzeling}
\author[8]{Laura Twardochleb}
\author[9]{Charles P. Hawkins}
\author[1]{Ralf B. Schäfer}
\affil[1]{Institute for Environmental Sciences, University of Koblenz-Landau, Landau, Germany}
\affil[2]{Centre for Applied Water Science, Institute for Applied Ecology, University of Canberra, Canberra, Australia}
\affil[3]{Institute of Hydrobiology and Aquatic Ecosystem Management, University of Natural Resources and Life Sciences Vienna (BOKU), Vienna, Austria}
\affil[4]{Department of Zoology, University of Otago, Dunedin, New Zealand}
\affil[5]{University of Lorraine, CNRS, LIEC, Metz, France}
\affil[6]{Department of Biology, Colorado State University, Fort Collins, USA}
\affil[7]{Environment Protection Authority Victoria, Applied Sciences Division, Macleod, Australia}
\affil[8]{Department of Fisheries and Wildlife, Michigan State University, East Lansing, USA}
\affil[9]{Department of Watershed Sciences and the Ecology Center, Utah State University, Logan, USA}
\date{}

@@

\begin{longtable}{m{2.5cm}|m{4cm}|m{7cm}}

@@

%\begin{tabular}
\specialcell{Grouping \\ feature} & Trait & Combined traits\\

@@

%\end{tabular}

@@

For our study aim of comparing the effects of different aggregation methods on trait\-environment relationship inference, we aggregated the traits of two of the harmonised datasets to the family level.
We used three different aggregation approaches: (1) direct aggregation of taxa to family level with either the median or mean, giving equal weight to every taxon. We denote these aggregation methods as \textit{direct\_agg\textsubscript{median}} and \textit{direct\_agg\textsubscript{mean}}, respectively; (2) stepwise aggregation, first to the genus level and subsequently to the family level with either the median or mean. This approach gives equal weights to each genus. Hereafter, we denote this aggregation type as \textit{stepwise\_agg\textsubscript{median}} or \textit{stepwise\_agg\textsubscript{mean}}, respectively; and (3) aggregation using a weighted mean approach, denoted as \textit{weighted\_agg}. This method weights each genus according to its number of species in the trait datasets, regardless of whether information was available for every used grouping feature (Figure \ref{fig:data_proc_overview}). When we refer to \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg} together we denote these methods as mean aggregation methods and when we refer to \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}} together, we denote these methods as median aggregation methods.

@@

\subsection*{Effects of harmonisation and trait aggregation on trait-environ\-ment relationship inferences}

To further evaluate the effects of grouping-feature harmonisation and trait aggregation on characterisation of trait–environment relationships, we repeated the analysis of \citet{szocs_effects_2014}, who studied the effects of anthropogenic salinisation on invertebrates in the River Werra in Germany. The River Werra has been subject to effluents from the potash industry since the mid- 20th century, which makes it a useful system for studying the responses of invertebrates and their trait compositions to salinisation (\cite{bathe_biological_2011}). \citet{szocs_effects_2014}  used redundancy analysis (RDA) to compare trait compositions among sites downstream and upstream to the salt discharge. Further details about the original study can be found in \citet{szocs_effects_2014}.

@@

\begin{table}[ht]
    \centering
    \caption{Number (Nr.) of taxa per harmonised dataset and per taxonomic level. Numbers in parenthesis show rounded relative frequencies in percent.} 
    \label{tab:tax_coverage}
    \begin{tabular}{l|c|c|c|c|c}
    \toprule[.1em]
    Dataset & Taxa (Nr.) & Aquatic insects (Nr.) & Species & Genus & Family \\ 
    \toprule[.1em]
    EU & 4601 & 3942 (86) & 3739 (81) & 704 (15) & 158 (3) \\ 
    NOA & 3753 & 3305 (88) & 2414 (64) & 1163 (31) & 176 (5)  \\ 
    AUS & 1402 & 1016 (72) & 564 (40) & 578 (41) & 260 (19) \\ 
    NZ & 478 & 443 (93) & 404 (85) & 47 (10) & 27 (6) \\ 
    \bottomrule
    \end{tabular}
\end{table}
\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
\centering
Abbreviations: EU, European; NOA, North American; AUS, Australian; NZ, New Zealand.
}
\end{minipage}

@@

\begin{table}[H]
    \centering
    \caption{Rounded percentage of entries that include 
    information for the individual grouping features
    shown per trait dataset.} 
    \label{tab:trait_coverage}
    \begin{tabular}{l|c|c|c|c|c|c|c}
    \toprule[.1em]
    Dataset & \specialcell{Body \\ form} & Oviposition & Voltinism & Locomotion & Size & Respiration & \specialcell{Feeding \\ mode} \\ 
    \toprule[.1em]
    EU & 8 & 15 & 23 & 36 & 11 & 57 & 76 \\ 
    NOA & 28 & 13 & 47 & 52 & 73 & 44 & 63 \\ 
    AUS & 4 & 46 & 49 & 39 & 75 & 68 & 99 \\ 
    NZ & 100 & 94 & 100 & 99 & 100 & 100 & 99 \\ 
    \bottomrule
    \end{tabular}
\end{table}
\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
\centering
Abbreviations: EU, European; NOA, North American; AUS, Australian; NZ, New Zealand.
}
\end{minipage}

@@

@@

\begin{landscape}
\begin{table}[H]
  \centering
  \caption{Percentage of differing cases, minimum, maximum, mean, and standard deviation of absolute differences between trait affinities assigned at family level by experts and aggregated trait affinities from five different aggregation methods.}
  \label{tab:summary_stat_aggr_vs_fam_assigned}
  \begin{tabular}{ll|ccccc}
  \toprule[.1em]
  Database & \specialcell{Comparison to\\ traits at family level} & \specialcell{Differing \\ cases [\%]} & \specialcell{Min. \\ differences} & \specialcell{Max. \\ differences} & \specialcell{Mean abs. \\ differences} & \specialcell{SD abs. \\ differences} \\ 
  \toprule[.1em]
  \multirow{4}{*}{\specialcell{Australia}} & \specialcell{\textit{direct\_agg (median)}} & 16.53 & 0.01 & 1.00 & 0.45 & 0.27 \\ 
  & \specialcell{\textit{direct\_agg (mean)}} & 23.24 & $< 0.01$ & 0.99 & 0.34 & 0.23 \\ 
  & \specialcell{\textit{stepwise\_agg (median)}} & 17.90 & 0.01 & 1.00 & 0.42 & 0.26 \\ 
  & \specialcell{\textit{stepwise\_agg (mean)}} & 23.24 & $< 0.01$ & 0.99 & 0.33 & 0.22 \\ 
  & \specialcell{\textit{weighted\_agg}} & 23.24 & $< 0.01$ & 1.00 & 0.34 & 0.24 \\ 
  \midrule
  \multirow{4}{*}{\specialcell{North America}} & \specialcell{\textit{direct\_agg (median)}} & 15.33 & 0.17 & 1.00 & 0.70 & 0.26 \\ 
  & \specialcell{\textit{direct\_agg (mean)}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.26 \\ 
  & \specialcell{\textit{stepwise\_agg (median)}} & 18.00 & 0.08 & 1.00 & 0.63 & 0.28 \\ 
  & \specialcell{\textit{stepwise\_agg (mean)}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.27 \\ 
  & \specialcell{\textit{weighted\_agg}} & 47.00 & $< 0.01$ & 1.00 & 0.31 & 0.28 \\ 
  \bottomrule
  \end{tabular}
\end{table}
\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
  \centering
  Abbreviations: Min., Minimum; Max., Maximum; abs., absolute; SD, Standard deviation.
  }
 \end{minipage}
\end{landscape}

@@

\subsection*{Effects of harmonisation and trait aggregation on trait-environ\-ment relationships}

@@

\section*{Author contribution}
R.B.S. and S.K. designed the study; B.J.K. and L.M. provided trait data for Australia; P.U-P. provided body form trait data for European and North American invertebrates; C.P.H., N.L.P., and L.T. provided trait data for North America; C.D.M. provided trait data for New Zealand;
B.J.K., A.S-K., C.D.M, W.G., N.L.P., L.M., and C.P.H. provided in depth information on trait data and discussed the procedure of analysis; S.K. conducted data processing and the statistical analyses.; S.K. wrote the manuscript; B.J.K, A-S.K., C.D.M, P.U-P., C.P.H., and R.B.S. discussed the results and provided suggestions on the manuscript.

### 2021-02-18 Paper/Flowchart/Flowchart_methods.tex
18.02: Formatting fixes

\begin{tikzpicture}
      %% Nodes
      \node(duplTaxa)[intstepsnode, align = center] at (-5cm,0cm){Consolidating duplicate \\ taxa in  EU, NOA, AUS \& \\ NZ databases};
      \node(normalAUS)[intstepsnode, align = center, xshift = 0cm, yshift = 0cm]{AUS traits standardised to [0 - 1] \\ because multiple codings used \\ throughout this database};
      \node(omission)[intstepsnode, align = center, xshift = 5cm, yshift = 0cm]{Omitted taxa less \\ precise than family-level};

@@

      \node(tab_aggregation)[xshift = -3cm, yshift = -6.6cm]{
        \begin{tabular}{ccc|ccc}
        Family & Genus & Species & \specialcell{Trait \\ A\_h\textsubscript{1}} & \specialcell{Trait \\ A\_h\textsubscript{2}} & \specialcell{Trait \\ A\_h\textsubscript{3}} \\
        \hline
         F\textsubscript{1} & G\textsubscript{1} & S\textsubscript{1} & 0.25 & 0.75 & 0\\
         F\textsubscript{1} & G\textsubscript{1} & S\textsubscript{2} & 0.5 & 0.5 & 0\\
         F\textsubscript{1} & G\textsubscript{1} & S\textsubscript{3} & 0.5 & 0.5 & 0 \\
         F\textsubscript{1} & G\textsubscript{2} & S\textsubscript{4} & 0 & 1.0 & 0 \\
         F\textsubscript{1} & G\textsubscript{2} & \textit{NA} & 0.25 & 0.75 & 0 \\
         F\textsubscript{1} & \textit{NA} & \textit{NA} & 0.25 & 0.75 & 0 \\
      \end{tabular}};

      \node(directAgg)[aggrtypesnode, align = center, xshift = 4cm, yshift = -5cm]{Direct aggregation};

      \node(tab_direct_agg)[xshift = 4cm, yshift = -7.5cm]{
        \begin{tabular}{c|ccc}
        Family & Trait & Method & Value \\
        \hline
        F\textsubscript{1} & A\_h\textsubscript{1} & mean & 0.29 \\
        F\textsubscript{1} & A\_h\textsubscript{2} & mean & 0.71 \\
        F\textsubscript{1} & A\_h\textsubscript{3} & mean & 0 \\
        \hline
        F\textsubscript{1} & A\_h\textsubscript{1} & median & 0.25 \\
        F\textsubscript{1} & A\_h\textsubscript{2} & median & 0.75 \\
        F\textsubscript{1} & A\_h\textsubscript{3} & median & 0 \\
      \end{tabular}};

      \node(stepwiseAgg)[aggrtypesnode, align = center, xshift = -3.5cm, yshift = -10.3cm]{Stepwise aggregation};

      \node(tab_stepwise_agg)[xshift = -3.5cm, yshift = -12.5cm]{
        \begin{tabular}{cc|ccc}
        Family &Genus & Trait & Method & Value \\
        \hline
        F\textsubscript{1}& G\textsubscript{1} & A\_h\textsubscript{1} & mean & 0.4167\\
        F\textsubscript{1}& G\textsubscript{2} & A\_h\textsubscript{1} & mean & 0.125\\
        F\textsubscript{1}& NA & A\_h\textsubscript{1} & - & 0.25\\
      \end{tabular}};

      \node(stepwiseAgg2)[aggrstepsnode, align = center, xshift = -3.5cm, yshift = -14.7cm]{ $A\_h_1 = mean(0.4167, 0.125, 0.25)$ \\ $ = 0.26$};

      \node(weightedAgg)[aggrtypesnode, xshift = 4cm, yshift = -10.3cm]{Weighted aggregation};

      \node(weights)[aggrstepsnode, align = center, xshift = 4cm, yshift = -12.7cm]{Weights based on \\ species per genera: \\
      $3$ for $G_1$, $1$ for $G_2$, \\
      weight for $F_1$ set to $1$};

      \node(weights2)[aggrstepsnode, align = center, xshift = 4cm, yshift = -15.1cm]{$A\_h_1 = \frac{0.25*3+0.5*3+...+ 0.25*1}{3+3...+1}$ \\ \\ $ = 0.35$};

>>>>

\begin{tikzpicture}
      %% Nodes
      \node(duplTaxa)[intstepsnode, align = center] at (-5cm,0cm){Consolidating duplicate \\ taxa in  EU, NOA, AUS \& \\ NZ databases};
      \node(normalAUS)[intstepsnode, align = center, xshift = 0cm, yshift = 0cm]{ Normalised AUS \\ traits ([0 - 1]) to work \\ with multiple codings};
      \node(omission)[intstepsnode, align = center, xshift = 5cm, yshift = 0cm]{Omitted taxa less \\ precise than family-level};

@@

      \node(tab_aggregation)[xshift = -3cm, yshift = -7.2cm]{
        \begin{tabular}{ccc|ccc}
        Family & Genus & Species & \specialcell{Trait \\ A\_h\textsubscript{1}} & \specialcell{Trait \\ A\_h\textsubscript{2}} & \specialcell{Trait \\ A\_h\textsubscript{3}} \\
        \hline
         F\textsubscript{1} & G\textsubscript{1} & S\textsubscript{1} & 0.25 & 0.75 & 0\\
         F\textsubscript{1} & G\textsubscript{1} & S\textsubscript{2} & 0.5 & 0.5 & 0\\
         F\textsubscript{1} & G\textsubscript{1} & S\textsubscript{3} & 0.5 & 0.5 & 0 \\
         F\textsubscript{1} & G\textsubscript{2} & S\textsubscript{4} & 0 & 1.0 & 0 \\
         F\textsubscript{1} & G\textsubscript{2} & \textit{NA} & 0.25 & 0.75 & 0 \\
         F\textsubscript{1} & \textit{NA} & \textit{NA} & 0.25 & 0.75 & 0 \\
      \end{tabular}};

      \node(directAgg)[aggrtypesnode, align = center, xshift = 4.2cm, yshift = -5cm]{Direct aggregation};

      \node(tab_direct_agg)[xshift = 4.2cm, yshift = -8.2cm]{
        \begin{tabular}{c|ccc}
        Family & Trait & Method & Value \\
        \hline
        F\textsubscript{1} & A\_h\textsubscript{1} & mean & 0.29 \\
        F\textsubscript{1} & A\_h\textsubscript{2} & mean & 0.71 \\
        F\textsubscript{1} & A\_h\textsubscript{3} & mean & 0 \\
        \hline
        F\textsubscript{1} & A\_h\textsubscript{1} & median & 0.25 \\
        F\textsubscript{1} & A\_h\textsubscript{2} & median & 0.75 \\
        F\textsubscript{1} & A\_h\textsubscript{3} & median & 0 \\
      \end{tabular}};

      \node(stepwiseAgg)[aggrtypesnode, align = center, xshift = -3.5cm, yshift = -11.3cm]{Stepwise aggregation};

      \node(tab_stepwise_agg)[xshift = -3.5cm, yshift = -13.6cm]{
        \begin{tabular}{cc|ccc}
        Family &Genus & Trait & Method & Value \\
        \hline
        F\textsubscript{1}& G\textsubscript{1} & A\_h\textsubscript{1} & mean & 0.4167\\
        F\textsubscript{1}& G\textsubscript{2} & A\_h\textsubscript{1} & mean & 0.125\\
        F\textsubscript{1}& NA & A\_h\textsubscript{1} & - & 0.25\\
      \end{tabular}};

      \node(stepwiseAgg2)[aggrstepsnode, align = center, xshift = -3.5cm, yshift = -16cm]{ $A\_h_1 = mean(0.4167, 0.125, 0.25)$ \\ $ = 0.26$};

      \node(weightedAgg)[aggrtypesnode, xshift = 4.2cm, yshift = -11.3cm]{Weighted aggregation};

      \node(weights)[aggrstepsnode, align = center, xshift = 4.2cm, yshift = -13.4cm]{Weights based on \\ species per genera: \\
      $3$ for $G_1$, $1$ for $G_2$, \\
      weight for $F_1$ set to $1$};

      \node(weights2)[aggrstepsnode, align = center, xshift = 4.2cm, yshift = -16cm]{$A\_h_1 = \frac{0.25*3+0.5*3+...+ 0.25*1}{3+3...+1}$ \\ \\ $ = 0.35$};
